FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2018-05-02 ECOOP18/sections/Discussion.tex
finish fixing reviews. Ready for Bruno to check.

One non-orthogonal extension to \MIM{} could be to generalize the model to allow multiple hierarchical method overrding, meaning that, we allow overriding methods to update multiple branches instead of only one branch. We present the modification of syntax, typing and semantic rules below (abstract methods omitted):

@@

>>>>

One non-orthogonal extension to \MIM{} could be to generalize the model to allow multiple hierarchical method overrding, meaning that, we allow overriding methods to update multiple branches instead of only one branch. It offers a more fine-grained mechanism for merging, and can be helpful to easily understand the structure of the hierarchy. Multiple overriding would be useful in the following situation, for example:

\begin{lstlisting}
interface A { void m() {...} }
interface B { void m() {...} }
interface C { void m() {...} }
interface D extends A, B, C {
	void m() override A,B {...}   // overrides branches A and B only
	void m() override C {...}      // overrides branch C
}
\end{lstlisting}

Here \lstinline|D| inherits from three interfaces \lstinline|A, B, C| with
conflicting methods \lstinline|m|, but only merges two of those methods.
While we can simulate D without multiple overriding in our calculus
(by introducing an intermediate class), a better approach would be
to support multiple overriding natively.

We present the modification of syntax, typing and semantic rules below (abstract methods omitted):

@@

With this approach, branches \lstinline|A| and \lstinline|B| are merged in the sense that they share the same code, which can be separately updated in future interfaces. Another approach is to deeply merge the branches, with similar effect as introducing an intermediate interface \lstinline|AB| to explicitly merge the two branches. However, this approach is problematic because there is no clear mechanism of identifying and further updating the merged branches. This could be an interesting future work to explore.

### 2018-05-02 ECOOP18/sections/Formalization.tex
finish fixing reviews. Ready for Bruno to check.

\subsubsection{Interfaces}
In order to achieve multiple inheritance, an interface can have a set of 
parent interfaces, where such a set can be empty. The interface declaration $\interface{I}{I}{M}$ introduces an interface named $I$ with parent interfaces $\overline{I}$ and a suite of methods $\overline{M}$. The methods of $I$ may either override methods that are already defined in $\overline{I}$ or add new functionality special to $I$, we will illustrate this in more detail later.

>>>>

\subsubsection{Interfaces}
In order to achieve multiple inheritance, an interface (which is acyclic, by deafault) can have a set of 
parent interfaces, where such a set can be empty. The interface declaration $\interface{I}{I}{M}$ introduces an interface named $I$ with parent interfaces $\overline{I}$ and a suite of methods $\overline{M}$. The methods of $I$ may either override methods that are already defined in $\overline{I}$ or add new functionality special to $I$, we will illustrate this in more detail later.
